Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-04-11 emsoft-2019/Cont_Syn.tex
fixes for algorithm

\begin{figure}
\begin{lstlisting}[language=Python,numbers=left,numbersep=3pt,frame=lines,keepspaces=true,escapeinside={(*}{*)},basicstyle=\small\ttfamily]
 (*$\delta$*) = input()
 (*$\varepsilon_{Q}$*) = input()
 assert ((*$\delta$*) >= 0 and (*$\varepsilon_{Q}$*) > 0)
 (*$\varepsilon$*) = (*$\varepsilon_{A/D}$*) + (*$\varepsilon_{Q}$*)

 while True:
   F,G,H,K = design_robust_MPC((*$\delta$*))
   errorChoise = incorrect_region_error(F,G,H,K,(*$\varepsilon$*))
   if (*$\delta$*) > errorChoise:
     errorAct = (*$\delta$*) - errorChoise
     precision_tuning(F, G, errorAct)
     precision_tuning(H, K, (*$\varepsilon$*))
     break
   else:
     (*$\delta$*)=errorChoise+(*$\varepsilon_{SAFE}$*)
\end{lstlisting}
\caption{design of robust MPC with precision tuning}
\label{lst:alg}
\end{figure}

@@

In the previous section, we assumed a given precision $p$. In this section we
present our algorithm for deriving a suitable value of $p$ fully automatically.

\subsection{Algorithm}
\eva{This section needs to structure the explanation in the order in which it
appears in the algorithm (i.e. starting from the input and explaining why for
instance $\varepsilon_Q$ is an input), and should reference the lines in the
algorithm, not only the equations from the previous section}
\autoref{lst:alg} reports the optimization algorithm we implemented to build robust MPC controllers with guaranteed error bounds.

From line 1 to 3, the procedure waits for input parameters from the designer: $\delta$ and $\varepsilon_{Q}$. $\delta$ is the maximal disturbance coefficient the controller has to be designed for. It is a problem dependent parameter, and thus can be any positive number. Typically, it is in the order of 0.1.
$\varepsilon_{Q}$ is the imprecision error-bound for the quantization of borders. 
The latter has to be strictly greater than zero, otherwise we could rely on infinite precision for storage of borders. Usually, the value for $\varepsilon_{Q}$ is in the order of 0.001.

>>>>

\begin{figure}
\begin{lstlisting}[language=Python,numbers=left,numbersep=3pt,frame=lines,keepspaces=true,mathescape=true,basicstyle=\small\ttfamily]
 $\Delta$ = input()
 $\varepsilon_{Q}$ = input()
 assert ($\Delta$ >= 0 and $\varepsilon_{Q}$ > 0)
 $\varepsilon$ = $\varepsilon_{A/D}$ + $\varepsilon_{Q}$

 while true:
   F, G, H, K = design_robust_MPC($\Delta$)
   errorRegion = incorrect_region_error(F, G, H, K, $\varepsilon$)
   if $\Delta$ > errorRegion:
     errorAct = $\Delta$ - errorRegion
     $\hat{\text{F}}$, $\hat{\text{G}}$ = precision_tuning(F, G, errorAct)
     $\hat{\text{H}}$, $\hat{\text{K}}$ = precision_tuning(H, K, $\varepsilon$)
     return $\hat{\text{F}}$, $\hat{\text{G}}$, $\hat{\text{H}}$, $\hat{\text{K}}$
   else:
     $\Delta$ = errorRegion + $\varepsilon_{SAFE}$
\end{lstlisting}
\caption{Algorithm for designing memory-efficient robust EMPC controller}
\label{lst:alg}
\end{figure}

@@

In the previous section, we assumed a given precision $p$. In this section we
present our algorithm for deriving suitable values of $p$ fully automatically.
Further, while~\autoref{sec:Error_Analysis} assumed a uniform fixed-point precision,
our tuning algorithm derives possibly different precisions for different control
values.

\subsection{Algorithm}
\eva{This section needs to structure the explanation in the order in which it
appears in the algorithm (i.e. starting from the input and explaining why for
instance $\varepsilon_Q$ is an input), and should reference the lines in the
algorithm, not only the equations from the previous section}
\autoref{lst:alg} shows a high-level view of our optimization algorithm for
implementing robust MPC controllers with guaranteed error bounds.

\eva{\autoref{lst:alg} needs another input: state-space model which goes into the MPC designer}
\eva{Add here the explanation why $\varepsilon_Q$ is an input}
From line 1 to 3, the procedure waits for input parameters from the designer: $\delta$ and $\varepsilon_{Q}$. $\delta$ is the maximal disturbance coefficient the controller has to be designed for. It is a problem dependent parameter, and thus can be any positive number. Typically, it is in the order of 0.1.
$\varepsilon_{Q}$ is the imprecision error-bound for the quantization of borders. 
The latter has to be strictly greater than zero, otherwise we could rely on infinite precision for storage of borders. Usually, the value for $\varepsilon_{Q}$ is in the order of 0.001.
